Applying Multi-Core Model Checking to Hardware-Software Partitioning in Embedded Systems

### 2015-09-08 Docs/Paper/LaTex/template.tex
minor corrections

In~\cite{Trindade2015,Trindade2016,Trindade2014} was shown that it is possible to use Bounded Model Checking (BMC) based on Satisfiability Modulo Theories (SMT) to perform HW-SW partitioning in embedded systems. The present work extends those studies since there is a substantial improvement in terms of the SMT-based verification method, which has been extended with a multi-core binary-search approach, as well as, the integration of the $\nu$Z tool into ESBMC, which is a state-of-art optimization tool based on SMT~\cite{Bjorner2015}. Multi-core processors have been used in all segments of industry to implement high-performance computing~\cite{Wu2014}. In particular, hardware platforms, together with multi-processing platforms, have allowed verification algorithms to distribute tasks executions across multiple processors, which generate an increase in performance if compared to single-core solution~\cite{Holzmann11}. However, most algorithms for software verification still disregard the limitations of the CMOS technology and focus their solution on a single-core approach~\cite{Cordeiro2012,Clarke2004,Armando2009,Ganai2006}.

Here, we exploit the availability of multi-core processors; in particular, SMT-based verification methods are applied to the HW-SW partition problem in three different ways using multi-core ESBMC with OpenMP:  ESBMC-MC using a sequential-search, ESBMC-PS using a parallel-search, and ESBMC-PB using a binary-search. Experimental results are compared to ILP (integral linear programming), GA (generic algorithms) in a multi-core version, and also the $\nu$Z tool, which supports only a single-core approach~\cite{Bjorner2015}. The ILP and GA algorithms are implemented with the Optimization Toolbox of Matlab~\cite{OpenMP1998}, while $\nu$Z is a built-in tool to the SMT solver Z3 in which its main function is to check the satisfiability of logical formulas based on objective functions. All multi-core ESBMC with OpenMP approaches, together with $\nu$Z, are implemented with the Efficient SMT-based Bounded Model Checker (ESBMC) tool~\cite{Cordeiro2012}.

@@

%----------------------------------------------
\subsection{Multi-core ESBMC with OpenMP (ESBMC-MC)}
\label{Multi-core-ESBMC-with-OpenMP}
%----------------------------------------------

@@

\begin{itemize}
\item{\textbf{ESBMC:} This strategy uses only one core to solve the partitioning problem, as described in Section~\ref{Verification-Algorithm-using-ESBMC}.
\item{\textbf{ESBMC-MC:} This uses a sequential strategy \{1 ,2 ,\:...\:, Hmax\}; there is no parallel controller in this approach, as described in Section~\ref{Multi-core-ESBMC-with-OpenMP}.}
\item{\textbf{ESBMC-PS:} This approach is similar to ESBMC MC; however, it uses a more optimized way to launch the ESBMC instances, as described Section~\ref{Multi-core-ESBMC-with-OpenMP-using-workers}.}
\item{\textbf{ESBMC-PB:} This strategy uses a parallel binary search, as described in Section~\ref{Multi-core-ESBMC-with-OpenMP-using-Binary-Search}.}}
\end{itemize}

@@

%MultiCore ESBMC
\multirow{2}{*}{\textbf{ESBMC-MC}}
&  T(s)   &  2   &  6   &  7   &  1615   &  TO    &  TO   &  TO  \\
&  Hp   &  15   &  47   &  31   &  241   &  -    &  -   &  -  \\
\hline

>>>>

In~\cite{Trindade2015,Trindade2016,Trindade2014} was shown that it is possible to use Bounded Model Checking (BMC) based on Satisfiability Modulo Theories (SMT) to perform HW-SW partitioning in embedded systems. The present work extends those studies since there is a substantial improvement in terms of the SMT-based verification method, which has been extended with a multi-core parallel- and binary-search approaches, as well as, the integration of the MaxSMT solver $\nu$Z into ESBMC, which is a state-of-art optimization tool based on SMT~\cite{Bjorner2015}. Multi-core processors have been used in all segments of industry to implement high-performance computing~\cite{Wu2014}. In particular, hardware platforms, together with multi-processing platforms, have allowed verification algorithms to distribute tasks executions across multiple processors, which generate an increase in performance if compared to single-core solution~\cite{Holzmann11}. However, most algorithms for software verification still disregard the limitations of the CMOS technology and focus their solution on a single-core approach~\cite{Cordeiro2012,Clarke2004,Armando2009,Ganai2006}.

Here, we exploit the availability of multi-core processors; in particular, SMT-based verification methods are applied to the HW-SW partition problem in three different ways using a multi-core ESBMC approach with OpenMP: ESBMC-SS using a sequential-search (SS), ESBMC-PS using a parallel-search (PS), and ESBMC-PB using a binary-search (BS). Experimental results are compared to ILP (integral linear programming), GA (generic algorithms) in a multi-core version, and also to $\nu$Z, which supports only a single-core approach~\cite{Bjorner2015}. The ILP and GA algorithms are implemented with the optimization toolbox of Matlab~\cite{OpenMP1998}, while $\nu$Z is a built-in tool to the SMT solver Z3 in which its main function is to check the satisfiability of logical formulas based on objective functions. All multi-core ESBMC approaches with OpenMP, together with $\nu$Z, are implemented with the Efficient SMT-based Context-Bounded Model Checker (ESBMC) tool~\cite{Cordeiro2012}.

@@

%----------------------------------------------
\subsection{Multi-core ESBMC with OpenMP (ESBMC-SS)}
\label{Multi-core-ESBMC-with-OpenMP}
%----------------------------------------------

@@

\begin{itemize}
\item{\textbf{ESBMC:} This strategy uses only one core to solve the partitioning problem, as described in Section~\ref{Verification-Algorithm-using-ESBMC}.
\item{\textbf{ESBMC-SS:} This uses a sequential strategy \{1 ,2 ,\:...\:, Hmax\}; there is no parallel controller in this approach, as described in Section~\ref{Multi-core-ESBMC-with-OpenMP}.}
\item{\textbf{ESBMC-PS:} This approach is similar to ESBMC MC; however, it uses a more optimized way to launch the ESBMC instances, as described Section~\ref{Multi-core-ESBMC-with-OpenMP-using-workers}.}
\item{\textbf{ESBMC-PB:} This strategy uses a parallel binary search, as described in Section~\ref{Multi-core-ESBMC-with-OpenMP-using-Binary-Search}.}}
\end{itemize}

@@

%MultiCore ESBMC
\multirow{2}{*}{\textbf{ESBMC-SS}}
&  T(s)   &  2   &  6   &  7   &  1615   &  TO    &  TO   &  TO  \\
&  Hp   &  15   &  47   &  31   &  241   &  -    &  -   &  -  \\
\hline
